### 2016-06-30 Projects/DelCo_2012/Report/DelCo_2012.tex
update CAFS report

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_mid_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for Middle Position}
	\label{fig:CAFS_Water_mid}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for Back Position}
	\label{fig:CAFS_Water_full}
\end{figure}

@@

To further analyze the data, the temperature differences can be separated by each of the three thermocouples in the fire room. Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions2} shows the placement of three thermocouple arrays (TC A1, TC A2, and TC A3).
\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Instrumentation2}
	\caption{Schematic of  the Gas Cooling Experiments.}
	\label{fig:Gas_Cooling_Instrumentation_Dimensions2}
\end{figure}
Based on the monitor position (arrow at the doorway in Fig.~\ref{fig:Gas_Cooling_Instrumentation_Dimensions2}), thermocouple arrays A1 and A2 had more direct impact from the suppression agent compared to thermocouple array A3. Figure~\ref{fig:Burn_Building_Test_18b}, which shows the distribution of the water within the burn building from a spray density test for a straight stream with CAFS at the mid position, highlights the positions of the thermocouple trees.

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Bars/BB18b}
	\caption{Gas Cooling Spray Density Test 18}
	\label{fig:Burn_Building_Test_18b}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_A1_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for Thermocouple Tree A1}
	\label{fig:CAFS_Water_A1_all}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_A2_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for Thermocouple Tree A2}
	\label{fig:CAFS_Water_A2_all}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_A3_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for Thermocouple Tree A3}
	\label{fig:CAFS_Water_A3_all}
\end{figure}

% The data can be further divided to analyze the impact of the nozzle type on comparison between water and CAFS. Figures~\ref{fig:CAFS_Water_78_mid} and \ref{fig:CAFS_Water_SS_mid} show the results for 7 replicate comparisons of a 7/8~in. solid stream and 5 replicate comparisons of a straight stream respectively; both aimed at the middle position.

% \begin{figure}[!ht]
% 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/7_8_Solid_mid_scatter}
% 	\caption{CAFS vs Water Gas Cooling Comparison for 7/8~in. Solid Stream Mid Position}
% 	\label{fig:CAFS_Water_78_mid}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_mid_scatter}
% 	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Mid Position}
% 	\label{fig:CAFS_Water_SS_mid}
% \end{figure}

% The 7 replicate tests comparing water and CAFS from a 7/8~in. solid stream nozzle aimed at the middle position show a large bias towards water. For the 5 replicate tests with a straight stream nozzle, the least squared error line fit through the data falls along the edge of the measurement uncertainty bounds on the water side of comparison.

% The back position can also be decomposed to compare stream type. Figure~\ref{fig:CAFS_Water_SS_back} shows a single comparison between water and CAFS for a straight stream in the back position while Fig.~\ref{fig:CAFS_Water_Fog_back} shows a 2 replicate comparison between water and CAFS for a 30$^{\circ}$ Fog in the back position.

% \begin{figure}[!ht]
% 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_full_back_scatter}
% 	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Back Position}
% 	\label{fig:CAFS_Water_SS_back}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/30_Fog_full_back_scatter}
% 	\caption{CAFS vs Water Gas Cooling Comparison for 30$^{\circ}$ Fog Back Position}
% 	\label{fig:CAFS_Water_Fog_back}
% \end{figure}

% For the straight stream comparison (Fig.~\ref{fig:CAFS_Water_SS_back}), there is an inability to distinguish between the suppression agents with statistical confidence. The 30$^{\circ}$ Fog replicate comparison (Fig.~\ref{fig:CAFS_Water_Fog_back}) shows that CAFS has better cooling potential compared to water.

>>>>

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_mid_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for All Middle Position Replicates}
	\label{fig:CAFS_Water_mid}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for All Back Position Replicates}
	\label{fig:CAFS_Water_full}
\end{figure}

@@

To further analyze the data, the temperature differences can be separated by each of the three thermocouples in the fire room. Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions2} shows the placement of three thermocouple arrays (TC A1, TC A2, and TC A3).
\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Instrumentation2}
	\caption{Schematic of  the Gas Cooling Experiments.}
	\label{fig:Gas_Cooling_Instrumentation_Dimensions2}
\end{figure}
Based on the monitor position (arrow at the doorway in Fig.~\ref{fig:Gas_Cooling_Instrumentation_Dimensions2}), thermocouple arrays A1 and A2 had more direct impact from the suppression agent compared to thermocouple array A3. Figure~\ref{fig:Burn_Building_Test_18b} shows the distribution of the agent within the burn building from a spray density test for a straight stream with CAFS at the mid position compared to the positions of the thermocouple trees.
\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Bars/BB18b}
	\caption{Gas Cooling Spray Density Test 18}
	\label{fig:Burn_Building_Test_18b}
\end{figure}

There is a difference in the amount of direct impact from the suppression agent at the three spatial locations. Therefore, the maximum temperature differences for each thermocouple on the three different arrays should also be analyzed separately. Figures~\ref{fig:CAFS_Water_A1_all}, \ref{fig:CAFS_Water_A2_all}, and \ref{fig:CAFS_Water_A3_all} show the temperature cooling scatter for thermocouple trees A1, A2, and A3 respectively. Note that for thermocouple array A3, which has the least amount of direct suppression, the least squared error line is closest to the uniform impact line (black solid line) meaning that within the experimental uncertainty, water and CAFS are indistinguishable. Thermocouple array A3 also has the strongest statistical fit compared to arrays A1 and A2.

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_A1_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for All Thermocouple Tree A1 Replicates}
	\label{fig:CAFS_Water_A1_all}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_A2_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for All Thermocouple Tree A2 Replicates}
	\label{fig:CAFS_Water_A2_all}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_A3_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for All Thermocouple Tree A3 Replicates}
	\label{fig:CAFS_Water_A3_all}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_mid_A1_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for Middle Position Thermocouple Tree A1 Replicates}
	\label{fig:CAFS_Water_A1_mid}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_mid_A2_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for Middle Position Thermocouple Tree A2 Replicates}
	\label{fig:CAFS_Water_A2_mid}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_mid_A3_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for Middle Position Thermocouple Tree A3 Replicates}
	\label{fig:CAFS_Water_A3_mid}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_A1_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for Back Position Thermocouple Tree A1 Replicates}
	\label{fig:CAFS_Water_A1_back}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_A2_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for Back Position Thermocouple Tree A2 Replicates}
	\label{fig:CAFS_Water_A2_back}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_A3_scatter}
	\caption{CAFS vs Water Gas Cooling Comparison for Back Position Thermocouple Tree A3 Replicates}
	\label{fig:CAFS_Water_A3_back}
\end{figure}
